---
title: 'Performing Covering Analysis'
author: Wikum Dinalankara, Qian Ke, Luigi Marchionni
header-includes:
   - \usepackage{tabularx, longtable, graphicx, csquotes, hyperref, color, url}
output:
  pdf_document:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{Performing Divergence Analysis}
  %\VignetteEngine{knitr}
  \usepackage[utf8]{inputenc}
bibliography: lpcover.bib
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}

```

\section{Introduction}

This package provides functionality to provide 'covering' solutions as presented by [@KePaired]. This is a type of binary integer programming optimization, where given a series of samples represented by binary variables, we attempt to find a small subset of the variable indices such that a required proportion of samples have at least $r$ non-zero variables from the subset.  

Say we have $n$ samples $Z_i = (z_{i,g} \in \{0, 1\}), i=1..n, g \in G$. Here $G$ is a set of features. Then we would like to find the smallest set $J$ where $|J| \le |G|$ such that 

\[ \sum_{j \in J} z_{i,g} \ge r ~~~ \forall i, r > 0 \]

where we refer to $J$ as a minial $r$-covering of the samples $Z_i$. More generally, we can require the omission of an $\alpha$ proportion of samples from being covered so that we obtain the miniaml covering solution that covers at least $1-\alpha$ proportion of samples or more.

Then the optimization required is:

\[ minimize ~~~ \sum_{g \in G} x_g \]

such that

\[ \forall i ~~~ \sum_g x_g z_{i, g} \ge ry_i \]
\[ \sum_i y_i \ge (1-\alpha)|G| \]

where $x_g$ and $y_i$ are binary variables.


\section{Example}

The package provides a function `computeMinimalCovering()` to which the user can supply a binary matrix and required `alpha` and `r` values. Given that usually multiple optimal solutions are available, the user can request upto `maxsol` number of solutions. Either `Gurobi` or `lpSolve` packages can be used for optimization (where the preferred solver can be supplied in the `solver` argument), though we highly suggest using `Gurobi`, particularly for large problems since we have found `lpSolve` not adequately efficient for solving the optimization in a timely manner.

The function returns a list where the solutions are provided in a character matrix `sol`.

The following code provides an example of how to use the main function:

```{r, echo=TRUE}

#load package
library(lpcover)

result.optim = computeMinimalCovering(mat=mat, 
                                      alpha=0.9, 
                                      J=2, 
                                      maxsol=3, 
                                      solver="gurobi")

result.optim$sol

```


\section{Session Information}

```{r, echo=TRUE, warning=FALSE}

sessionInfo()

```

\section{References}






